### 2025-01-06 README.Rmd
replace interactive by images in readme #53

<iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario1.html" width="800" height="400px" data-external="1">

</iframe>

@@

<iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario2.html" width="800" height="400px" data-external="1">

</iframe>

@@

<iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario3.html" width="800" height="400px" data-external="1">

</iframe>

>>>>

<!--iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario1.html" width="800" height="400px" data-external="1"-->

<!--/iframe-->

![](images/clipboard-917840690.png)

@@

<!--iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario2.html" width="800" height="400px" data-external="1"-->

<!--/iframe-->

![](images/clipboard-2091156617.png)

@@

<!--iframe src="https://u-shift.github.io/biclarwww/lisboa/mapa_cenario3.html" width="800" height="400px" data-external="1"-->

<!--/iframe-->

![](images/clipboard-1852439731.png)
